Safe Memory Regions for Big Data Processing

### 2016-10-21 paper/introduction.tex
minor fixes

Our inference algorithm proceeds in three stages: in the first stage,
we elaborate the program by introducing region parameters (for classes and methods);
in the second stage we generate a set of constraints that must be satisfied for
the program to type check; in the third stage, we solve the set of constraints,
inferring the preconditions of all classes and methods (in terms of the
expected outlives-constraints between the region parameters).
We show that the second and third stages are sound as well as
complete (while the first stage is sound).
% (using an interprocedural fixed point computation).
% While the first

>>>>

Our inference algorithm proceeds in three stages: in the first stage,
we elaborate the program by introducing region parameters (for classes and methods);
in the second stage we generate a set of constraints that must be satisfied for
the program to type check; in the third stage, we solve the set of constraints,
inferring the preconditions of all classes and methods (in terms of the
expected outlives-constraints between the region parameters).
We show that the second and third stages are sound as well as
complete (while the first stage is sound).
% (using an interprocedural fixed point computation).

\paragraph{Evaluation.}
Our work was inspired by~\cite{Broom:HotOS}, which presents evidence that
realistic programs can be written using transferable regions
and that this can yield significant performance improvements.
The system described in~\cite{Broom:HotOS}, however, provides no memory
safety guarantees, which is the subject of our contribution.
We report on an implementation of our type inference algorithm that
was able to identify some unsafe memory accesses and was able to successfully
verify programs correct (once the errors were fixed).

### 2016-10-21 paper/type-inference.tex
minor fixes

Fig.~\ref{fig:constraint-gen-0} illustrates this for selected language constructs.
These rules use the same context as the corresponding typing judgment in
Fig.~\ref{fig:fb-staticsem}, except that this is generalized to permit the
use of region variables and predicate variables.
Symbols $\A$ and $\env$ retain their meaning, modulo this extension.
The algorithm proceeds top-down, analyzes an expression $e$ in a context
$\stdcontext$, and returns a type $\tau$ and a set of constraints $C$
(expressed in the rules as $\exprok {\stdcontext} {e} {\tau} {C}$ ),
indicating that the expression will have a type $\tau$ provided the constraints $C$ hold.

>>>>

Fig.~\ref{fig:constraint-gen-0} illustrates this for selected language constructs.
(The appendix contains the remaining constraint generation rules.)
These rules use the same context as the corresponding typing judgment in
Fig.~\ref{fig:fb-staticsem}, except that this is generalized to permit the
use of region variables and predicate variables.
Symbols $\A$ and $\env$ retain their meaning, modulo this extension.
The algorithm proceeds top-down, analyzes an expression $e$ in a context
$\stdcontext$, and returns a type $\tau$ and a set of constraints $C$
(expressed in the rules as $\exprok {\stdcontext} {e} {\tau} {C}$ ),
indicating that the expression will have a type $\tau$ provided the constraints $C$ hold.

Note that some of the conditions in the antecedents are checked at constraint-generation
time, while some are encoded as constraints (to be resolved by the constraint-solver).
E.g., we assume that the region constants introduced by
\C{open}
and
\C{letregion}
constructs are unique (and the elaboration phase ensures this by alpha-renaming
them as needed). Thus, the precondition $\rho \not\in \Delta$ in rules \textsc{LetRegion}
and \textsc{Open} merely validates this at constraint-generation time.
